Smoking and COVID Living Review (v8): a bayesian analysis

### 2020-11-02 reports/bayesian_report.Rmd
v9

---
title: 'Smoking and COVID Living Review (v7): a bayesian analysis'
author: "David Simons, Lion Shahab, Jamie Brown and Olga Perski"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output:

@@

```{r load_scripts}
source(here("scripts", "author_dictionary.R"))
```
## Download data
``` {r google_data}
sheets_id <- as_sheets_id("https://docs.google.com/spreadsheets/d/1sTlqMbGiWDWJT3dTpa3YQU4z6qcWb0v6Wkp40RcWLXQ/edit?usp=sharing")
search_details <- read_sheet(sheets_id, range = 'article_screening')
data_study_general <- read_sheet(sheets_id, range =  'general_details')
table_1 <- read_sheet(sheets_id, sheet = 'pop_descriptives')
table_2 <-  read_sheet(sheets_id, sheet = 'testing')
table_3 <-  read_sheet(sheets_id, sheet = 'hospitalisation')
table_4 <-  read_sheet(sheets_id, sheet = 'severity')
table_5 <-  read_sheet(sheets_id, sheet = 'mortality')
table_6 <-  read_sheet(sheets_id, sheet = 'updated_quality_appraisal')
```
We maintain a Google sheets document [here](sheets_id) which contains all eligible articles the research team have identified. This is currently viewable only and not open for editing. We have collected the general information for the search in the first sheet, the studies general information in the second, further information on study populations, outcomes of interest and quality of the studies are contained in the further sheets. These sheets are organised in a similar way to the manuscript and so are labelled table_1 to table_6.

@@

exclude_from_analysis <- c(superseded_studies, old_isaric, excluded_other_reason)
```
We don't want to remove studies from the dataset despite them no longer being included in the analysis. The excluded studies are defined in this chunk of code. We have excluded this version the following studies:
-`r knitr::combine_words(exclude_from_analysis)`
Generally we label these as _old in the Google sheet but there are exceptions to this so we manually define them at the moment.

## Filter the included studies
Based on the version and excluded studies we produce the tables for analysis. This is a searchable table.
``` {r descriptives}
data_study_general <- data_study_general %>%
  filter(review_version %in% analysed_versions) %>%
  filter(!(lead_author %in% exclude_from_analysis)) %>%
  write_rds(., here::here('data_clean', 'data_study_general.rds'))

@@

```
We have split the data into a list where each country can be analysed separately if required

Confidence intervals are obtained through bootstrap estimates of a thousand repetitions of the included studies. Following the production of the confidence intervals from bootstrapping in `olgas_script.R` the prevalence graphs are produced in the `smoking_plots.R` script. This uses data extracted on current and former smoking prevalence data from countries which have included studies in this review.

## Graph for smoking prevalence
**Current smoking prevalence**
The studies are grouped by the country in which they were conducted. The solid line represents national current smoking prevalence obtained from national smoking survey estimates. Studies are further grouped by the setting in which they were conducted, Hospital (Triangle), Community (Square) and Community and Hospital (Circle). The size of the shape corresponds to the relative size of the study sample. The weighted mean current smoking prevalence is displayed for each setting.
![Country smoking prevalence](figure/current_smoking_plots_updated.png)

@@

## Study quality assessment
``` {r table_6}
#Table 6
fair <- filter(quality_rating, quality_rating$overall_quality == "fair" ) %>%
  filter(!lead_author %in% exclude_from_analysis) %>%
  nrow()
poor <- filter(quality_rating, quality_rating$overall_quality == "poor" ) %>%
  filter(!lead_author %in% exclude_from_analysis) %>%
  nrow()
```
The number of **Fair** quality studies are `r paste(fair)` with `r paste(poor)` **Poor** quality studies

>>>>

---
title: 'Smoking and COVID Living Review (v8): a bayesian analysis'
author: "David Simons, Lion Shahab, Jamie Brown and Olga Perski"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output:

@@

```{r load_scripts}
source(here("scripts", "author_dictionary.R"))
```
## Download data
``` {r google_data}
sheets_id <- as_sheets_id("https://docs.google.com/spreadsheets/d/1yLtpbk29oUKOGceVw2IAJlt9CbbbPWmltzOW_LG6Su8/edit?usp=sharing")
search_details <- read_sheet(sheets_id, range = 'article_screening')
data_study_general <- read_sheet(sheets_id, range =  'general_details')
table_1 <- read_sheet(sheets_id, sheet = 'pop_descriptives')
table_2 <-  read_sheet(sheets_id, sheet = 'testing')
table_3 <-  read_sheet(sheets_id, sheet = 'hospitalisation')
table_4 <-  read_sheet(sheets_id, sheet = 'severity')
table_5 <-  read_sheet(sheets_id, sheet = 'mortality')
table_6 <-  read_sheet(sheets_id, sheet = 'updated_quality_appraisal')
```
We maintain a Google sheets document [here](sheets_id) which contains all eligible articles the research team have identified. This is currently viewable only and not open for editing. We have collected the general information for the search in the first sheet, the studies general information in the second, further information on study populations, outcomes of interest and quality of the studies are contained in the further sheets. These sheets are organised in a similar way to the manuscript and so are labelled table_1 to table_6.

@@

exclude_from_analysis <- c(superseded_studies, old_isaric, excluded_other_reason)
```
We don't want to remove studies from the dataset despite them no longer being included in the analysis. The excluded studies are defined in this chunk of code. We have excluded this version the following studies:

`r knitr::combine_words(exclude_from_analysis)`

Generally we label these as _old in the Google sheet but there are exceptions to this so we manually define them at the moment.

## Filter the included studies
Based on the version and excluded studies we produce the tables for analysis.

This is a searchable table.
``` {r descriptives}
data_study_general <- data_study_general %>%
  filter(review_version %in% analysed_versions) %>%
  filter(!(lead_author %in% exclude_from_analysis)) %>%
  write_rds(., here::here('data_clean', 'data_study_general.rds'))

@@

```
We have split the data into a list where each country can be analysed separately if required.

Prevalence graphs are produced in the `smoking_plots.R` script. This uses data extracted on current and former smoking prevalence data from countries which have included studies in this review. We calculate the mean weighted prevalence.

## Graph for smoking prevalence
**Current smoking prevalence**
The studies are grouped by the country in which they were conducted. The dashed line represents national current smoking prevalence obtained from national smoking survey estimates. The size of the shape corresponds to the relative size of the study sample. The weighted mean current smoking prevalence is displayed for each setting.

![Country smoking prevalence](figure/current_smoking_plots_updated.png)

@@

## Study quality assessment
``` {r table_6}
#Table 6
good <- filter(quality_rating, quality_rating$overall_quality == "good" ) %>%
  filter(!lead_author %in% exclude_from_analysis) %>%
  nrow()
fair <- filter(quality_rating, quality_rating$overall_quality == "fair" ) %>%
  filter(!lead_author %in% exclude_from_analysis) %>%
  nrow()
poor <- filter(quality_rating, quality_rating$overall_quality == "poor" ) %>%
  filter(!lead_author %in% exclude_from_analysis) %>%
  nrow()
```
The number of **Good** quality studies are `r paste(good)`, **Fair** quality studies are `r paste(fair)` with `r paste(poor)` **Poor** quality studies
